% What's the problem?
% Why is it a problem? Research gap left by other approaches?
% Why is it important? Why care?
% What's the approach? How to solve the problem?
% What's the findings? How was it evaluated, what are the results, limitations, 
% what remains to be done?

\paragraph{The problem}

We have a module on authentication for an introductory course on security.
During the learning activities we particularly cover the badness of requiring 
complex passwords.
Yet, on the exam we still find students who say that complex passwords is a 
good idea.
This has prompted us to ask the questions:
\begin{rqs}
\item%\label{rq-nochange}
  Why do some students retain their old behaviour despite the course module?

\item%\label{rq-unlearn}
  How can we make them unlearn something very reinforced and relearn the 
  correct?

\item%\label{rq-retention}
  How can we improve how long do the students retain what they have 
  (re)learned?
\end{rqs}

\paragraph{Who we support}

We primarily want to support the teacher, to evaluate and improve the learning 
design, thus indirectly supporting the students.
\Eg the inquiry might lead to a finding saying we need better feedback for 
students, to make them aware they haven't learned what they should have.

\paragraph{What learning activities we address}

The module is part of an online course.
The module consists of a flipped classroom session (six videos, one interactive 
session online) and a workshop assignment (two online seminars interleaved with 
paper reading and laboratory work).

\paragraph{Data we need and how to collect them}

We will use \ac{LA} to record how the students access the resources and the 
groups they work in.
This can be recorded with the tools used: \ac{VLE}, video meeting tool.
We use the assessment of the course to record how the students perform.
We will also conduct interviews to study the more qualitative aspects of the 
students' behaviour and reasons for the outcomes.

\paragraph{Motivation for the analysis}

We must analyse the \ac{LA} data to distinguish patterns that can guide our 
investigation.
The nature of \cref{rq-nochange} require qualitative data to explain the 
patterns that we might see.
That need is provided by the interviews.
The interviews can also guide us for \cref{rq-unlearn,rq-retention}.
The assessment of the course will tell us whether our learning design for 
\cref{rq-unlearn} succeeded or not.
Finally, to assess retention (\cref{rq-retention}), we must follow up with the 
students.

