\section{What's the approach?}
% What's the approach? How to solve the problem?

We take \iac{DBR} approach to investigate the research questions.
\Cref{rq-nochange} focuses on an initial problem that is expected to give some 
guidance to the answers of \cref{rq-unlearn,rq-retention}.
\Cref{rq-unlearn,rq-retention} require iterations, particularly to improve the 
retention of \cref{rq-retention}.

\paragraph{Learning analytics}

We will record when (or if) students access the resources in the course:
videos,
instructions,
papers,
\etc.
The \ac{VLE} records this, some parts are recorded by ScalableLearning and 
YouTube.
This data can potentially allow us to identity patterns.
\Eg we may see if the students still exhibiting the old behaviour did not take 
part of the prescribed material and simply didn't study.

However, there is still the possibility that they take part of the material 
second-hand through friends.
The students work in groups to prepare for seminars, do lab work \etc.
We record these group memberships: the students sign up for a group in the 
\ac{VLE}.
However, we cannot track how students communicate during preparations, since 
they do that in the real world during their own time.
But if we know the group memberships, we know at least who has 
\emph{potentially} communicated with whom.
We have previously observed that if they study together, one person in the 
group downloads the paper and prints or transmits a copy to the others.
But if we have the group memberships from above to see if such an explanation 
is possible for any individual student.

During seminars, there are also group discussions, but these groups are 
randomly assigned.
These group memberships must also be recorded: we record them manually using 
the online meeting tool during any seminar session.

We note again, this recorded data can only represent possibilities, not 
certainties.

\paragraph{A priori and a posteriori knowledge and motivation}

We also want to evaluate any change in the students induced by the learning 
activities.
For this, we must evaluate the students' knowledge and motivation a priori to 
the module and a posteriori.

In the first round\footnote{%
  Since this is part of \iac{DBR} project, we will do this several times.
} we will do this by semi-structured interviews, refining 
towards structured interviews for each iteration.
Before the module starts, we will conduct interviews with a random sample of 
students.
During this interview we want to evaluate the student's
\begin{itemize}
  \item attitude towards and emotional engagement with the subject,
  \item knowledge and beliefs related to the subject.
\end{itemize}

After the module, we will conduct the same interview again, to evaluate the 
possible change.

\paragraph{Ground truth}

Since we cannot tell from the \ac{LA} data whether they didn't study or they 
accessed the material through their peers, we must inquire about this too.
We will do this by interviewing select individuals exhibiting the behaviour.
However, these interviews will take place after the course has ended and their 
grades are set, to decrease any fear of affecting their grade and potentially 
increase the level of honesty.

What we are interested to learn from these interviews is
\begin{itemize}
  \item whether the student accessed the material second hand, when our records 
    indicate that the student didn't,
  \item whether the student didn't study the material despite the fact that the 
    student accessed it.
\end{itemize}
